---
title: "HW5"
author: "Brandon Simelgor"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
str(choco)
library(ggplot2)
```

### Question set 1

1. What is the overall number of chocolate bars rated?
```{r}
length(choco$Rating)
```
The overall number of chocolate bars rated is 1852.

2.How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
ggplot(choco, aes(x = Review.Date)) + geom_bar()
```

The more recent the year had higher ratings than older years, except for in 2015 when the ratings decreased again.

# Question set 2
1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram()
```

The distribution is slightly left skewed, the center is around 3 and is unimodal with some outliers at 1 and 5.

2. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
ggplot(choco, aes(x = Cocoa.Pct, y = Rating)) + geom_jitter()
```

In the graph we can see that the percentage of cocoa does not change the ratings as their does ont appear to be any real correlation.

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
```{r}
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot( top3, 
       aes(x = Company.Location, y = Rating)) + geom_boxplot()
```

Based on the graph we can see that out of the these three countries they all have a similar median near 3.25, but Canada has the highest upper quatrile while USA and Frances are similar, USA has the lowest lower quartile while Canada and Frances are similar.
