---
title: "HW5-DS"
author: "Evan Behrens"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
choco<-read.csv("choco.csv")
str(choco)
```
#  Question set 1

1)What is the overall number of chocolate bars rated?
```{r}
length(choco$Rating)
```
there are 1852 chocolate bars that have a rating


2)How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
ggplot(choco , aes(x =Review.Date))+geom_bar() 
```


There was a steady increase in number of chocoaltes reviewed over the years and thenin 2015 the number of ratings decreased again.



#  Question set 2

Question 1
How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r}
ggplot(choco, aes(x= Rating))+geom_histogram(bins = 15)
```


The distrubution of the ratings of chocolate bars is a little skewed to the left but almost normal, the center is around 3 and it is unimodal.The range spans from 1-5 and there appears to be an outlier at about a 5 rating, there could be outliers around 1 as well.


Do ratings depend on the cocoa percentage of a chocolate bar?


```{r}
ggplot(choco, aes(x = Cocoa.Pct, y = Rating))+geom_jitter()
```
There does not appear to be any real correltation between cocoa percentage and its rating. The correlation plot does not appear to be strong nor poisitve or negative.

How do ratings compare across different company locations? Focus on the three locations with the most ratings:


This plot below is not useful to look at 
```{r}
ggplot(choco , aes(x = Company.Location, y = Rating))+geom_boxplot()+coord_flip()
```


```{r}
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot( top3, 
       aes(x = Company.Location, y = Rating)) + geom_boxplot() 


```




The ratings between these three locations is interesting. They all have a similar median around 3.25 but Canadas upper quartile goes up to 3.75  while france and USA only go to 3.5. Both Canada and USA have a range of 2 while france only has a range of 1.5. France and the USA have an outlier/s.
