---
title: "LAB2"
author: "Andres Gonzalez"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
str(choco)
library(ggplot2)
```


### Question set 1

1. What is the overall number of chocolate bars used?

```{r}
length(choco$Rating)
```
There is 1852 bars used.

2.How does the number of ratings depend on the year? Draw a bar chart of the number of reports?

The more recent the year had more ratings than older years, except for 2017.
```{r}
ggplot(choco, aes(x = Review.Date)) + geom_bar()
```

# Question set 2
1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

The ratings more around 3 with outliers at 1 and 5.

```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram()
```

2. Do ratings depend on the cocoa percentage of a chocolate bar?

Ratings do not depend on the percentage of cocoa because in the graph we 
see that most of them get the same rating regardless of the cocoa percentage.

```{r}
ggplot(choco, aes(x = Cocoa.Pct, y = Rating)) + geom_jitter()
```

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:

we see that there are higher ratings in canada, france is ratings that are in the middle, and The united states has ratings that lower than both canada and france.

```{r}
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot( top3, 
       aes(x = Company.Location, y = Rating)) + geom_boxplot()
```

