---
title: "Team file"
author: "Andres Gonzalez, Evan brehrens, Brandon Simelgor"
date: "2023-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
str(choco)
library(ggplot2)
```

# Andres Question
The analysis I made from this data is comparing the ratings of the chocolate to the broad bean origin and seeing which origin of bean gives the highest ratings. From my barplot, we can see that Venezuela has the most instances of 4.0 rating with 18 data entries. When making this analysis I decided to just look at the top rated chocolates so I only looked at data entries that had a 4.0 rating.
```{r}
origin <- choco[c("Broad.Bean.Origin", "Rating")]
topO <- origin[origin$Rating == 4,]
```

```{r}
par(mar=c(7, 4.2, 4.2, 2.4))
barplot(table(topO$Broad.Bean.Origin), las=2, cex.names=0.55)
title(main="Top Places of Origin", xlab="", ylab="Count")
mtext(text = 'Country of Origin',side=1, line= 5.5)
```
```{r}
top_origin <- sum(topO == 'Venezuela')
top_origin
```

