---
title: "Team file"
author: "Andres Gonzalez, Evan behrens, Brandon Simelgor"
date: "2023-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
str(choco)
library(tidyverse)
library(ggplot2)
```

# Andres Question
My question was which broad bean origin had the highest ratings? From my barplot, I found that Venezuela had the most highest ratings with 20 "4" ratings. When making this analysis I decided to just look at the top rated chocolates so I only looked at data entries that had a 4.0 rating.

```{r}
choco_filtered <- choco %>% filter(Rating==4)
head(choco_filtered)
ggplot(choco_filtered, aes(y = Broad.Bean.Origin)) + geom_bar()
```

# Evan's Question
What was the most common cocoa percentage in a 4 rating?

I found that the most common percentage of cocoa used in chocolates rated 4 was right around 70. There are outliers at 60 and 90

```{r}
ggplot(choco_filtered, aes(x = Cocoa.Pct)) +
  geom_histogram(bins = 20) +xlab("Cocoa Percent") +ylab("Count") +ggtitle("Cocoa Percentages From Rated 4 Chocolates")


```

# Brandon's Question
Which company most commonly recieved a 4 rating?

I found their were two companys that recieved a 4 far more ferequently than any other company and those were Smooth Chocloter, with 10 The and Beschle (Felchlin) with 8 ratings.

```{r}
ggplot(choco_filtered, aes(x = Company)) + geom_bar() + theme (axis.text.x = element_text(angle = 90))

```


# Conclusion
The workflow was very smooth. All of us were able to come up with our own questions and answer them using graphs, ggplot and filter out certain data. We used to git and were able to pull and push our data whenever one of us edited the document. we all uploaded our own work into the repository without issue. The workflow was smooth the whole time.